%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Trainer} % Job title
    {SDA - Software Development Academy} % Organization
    {Rabat, Morocco} % Location
    {Aug. 2021 - Present (Part-time)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Trained classrooms of different students on development subjects.}
        \item {Organize workshops and implement projects.}
        \item {Monitor the progress of the classroom and strenghten the students' skills.}
        \item {Review the code quality and the best practices for advanced students.}
        \item {Used technologies: HTML, CSS, JavaDcript, SASS, Tailwind, Typescript, React, Redux Toolkit, Angular, RxJS, Git,}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Technical Lead} % Job title
    {4D SAS} % Organization
    {Rabat, Morocco} % Location
    {May 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assist team member with feature delivery.}
        \item {Review merge requests for code validity and conformity.}
        \item {Help with spec definition in different parts of the project.}
        \item {Assist with technical and architectural decisions.}
        \item {Develop automations for different secionts: CI/CD, code generation, migration scritps, ...etc}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Fullstack Software Engineer} % Job title
    {4D SAS} % Organization
    {Rabat, Morocco} % Location
    {Dec. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop web applications.}
        \item {Implementation of a LSP client to provide language features like auto complete, go to definition, find all references of a proprietary language.}
        \item {Develop Components for app building in Webstudio and insure the ability to communicate with the server using datasources.}
        \item {Develop and Manage a sub module responsible for defining database structures with DnD.}
        \item {Implement complex UX use cases in many different areas.}
        \item {Used technologies: Typescript, React, Redux Toolkit, 4D, React Testing Library, Jest, Cypress, Gatsby, Gitlab CI/CD, Docker, Craco, Tailwind, CraftJS, Git, Perforce, TeamCity, Husky}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
